Staged Abstract Interpreters

### 2019-09-10 paper/paper.tex
space
revision
title and subsection titles

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\documentclass[acmsmall,review]{acmart}\settopmatter{}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

\setcopyright{rightsretained}
\acmJournal{PACMPL}
\acmYear{2019} 
\acmVolume{3} 
\acmNumber{OOPSLA} 
\acmArticle{126} 
\acmMonth{10} 
\acmPrice{}\acmDOI{10.1145/3360552}

@@

%% Title information
%\title{Staged Abstract Interpreters}         %% [Short Title] is optional;
\title{Staged Abstract Interpreters}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Fast and Compositional Whole-Program Analysis for Free}                     %% \subtitle is optional
\subtitle{Fast and Modular Whole-Program Analysis via Meta-Programming}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Keywords
%% comma separated list
% \keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

@@

\iffalse

\renewcommand\thefootnotecopyrightpermission{}
\footnotetextcopyrightpermission{
Preprint, November 2018.\\ Copyright held by the authors.}
\fancyhead[RO,LE]{Preprint, November 2018}

\fi

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
\documentclass[acmsmall, screen]{acmart}\settopmatter{}

@@

\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3360552}
\acmYear{2019}
\copyrightyear{2019}
\acmJournal{PACMPL}
\acmVolume{3}
\acmNumber{OOPSLA}
\acmArticle{126}
\acmMonth{10}

@@

%% Title information
%\title{Staged Abstract Interpreters}         %% [Short Title] is optional;
\title{Staged Abstract Interpreters}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Fast and Compositional Whole-Program Analysis for Free}                     %% \subtitle is optional
\subtitle{Fast and Modular Whole-Program Analysis via Meta-programming}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Keywords
%% comma separated list
\keywords{multi-stage programming, abstract interpreters, control-flow analysis}  %% \keywords are mandatory in final camera-ready submission

@@
